Looking at Non-Linear Dimension Reductions as Models in the Data Space

### 2024-07-19 paper.qmd
Changed color in NLDR layouts

nldr_scurve <- umap_scurve_scaled |> 
  ggplot(aes(x = UMAP1, y = UMAP2)) + 
  geom_point(alpha=0.5, colour="#000000", size = 0.5) +
  xlim(sc_xlims) + ylim(sc_ylims) +
  interior_annotation("a", sc_ltr_pos)
```

@@

hex_grid_scurve <- ggplot(
  data = hex_grid_with_counts, 
  aes(x = x, y = y)) +
  geom_polygon(color = "black", 
               aes(group = hex_poly_id), 
               fill = "#ffffff") +
  geom_point(data = umap_scurve_scaled, 
             aes(x = UMAP1, y = UMAP2), 
             alpha = 0.5, size = 0.5) +
  xlim(sc_xlims) + ylim(sc_ylims) +
  interior_annotation("b", sc_ltr_pos)
```

@@

umap_pbmc <- umap_pbmc_scaled |>
  ggplot(aes(x = UMAP1,
             y = UMAP2)) +
  geom_point(alpha=0.5) 
```

@@

tsne_pbmc <- tsne_pbmc_scaled |>
  ggplot(aes(x = tSNE1,
             y = tSNE2)) +
  geom_point(alpha=0.5)
```

>>>>

nldr_scurve <- umap_scurve_scaled |> 
  ggplot(aes(x = UMAP1, y = UMAP2)) + 
  geom_point(alpha=0.5, colour="#6a3d9a", size = 0.5) +
  xlim(sc_xlims) + ylim(sc_ylims) +
  interior_annotation("a", sc_ltr_pos)
```

@@

hex_grid_scurve <- ggplot(
  data = hex_grid_with_counts, 
  aes(x = x, y = y)) +
  geom_polygon(color = "black", 
               aes(group = hex_poly_id), 
               fill = "#ffffff") +
  geom_point(data = umap_scurve_scaled, 
             aes(x = UMAP1, y = UMAP2), 
             alpha = 0.5, size = 0.5, color = "#6a3d9a") +
  xlim(sc_xlims) + ylim(sc_ylims) +
  interior_annotation("b", sc_ltr_pos)
```

@@

umap_pbmc <- umap_pbmc_scaled |>
  ggplot(aes(x = UMAP1,
             y = UMAP2)) +
  geom_point(alpha=0.3, color = "#6a3d9a") 
```

@@

tsne_pbmc <- tsne_pbmc_scaled |>
  ggplot(aes(x = tSNE1,
             y = tSNE2)) +
  geom_point(alpha=0.3, color = "#6a3d9a")
```
